---
title: "Untitled"
author: "Lamiae Harara"
date: "7/10/2021"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,message=FALSE,warning=FALSE}
#Libraries needed
library(dplyr)
library(ggplot2)
library(tinytex)
library(readxl)
library(GGally)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(GGally)
library(tidyr)
library(knitr)
library(ggfortify)
```

```{r}
#Load in our dataset 
# setwd("C:/Users/sony/Desktop/Rmarkdown")
happy_21<- read_xlsx("happiness.xlsx")
```


## Table Of Content

* Introduction
* Dataset Description

## Introduction

 
The World Happiness Report is a landmark survey of the state of global happiness .
The report continues to gain global recognition as governments, organizations and civil society increasingly use happiness indicators to inform their policy-making decisions. Leading experts across fields – economics, psychology, survey analysis, national statistics, health, public policy and more – describe how measurements of well-being can be used effectively to assess the progress of nations. The reports review the state of happiness in the world today and show how the new science of happiness explains personal and national variations in happiness.  
 

 
## Dataset Description

\normalsize

The happiness scores and rankings use data from the Gallup World Poll . The columns following the happiness score estimate the extent to which each of six factors 
- **Economic production
- **Social support
- **Life expectancy
- **Freedom
- **Absence of corruption
- **Generosity 


## Dataset

```{r echo = FALSE, warning=FALSE,message=FALSE}
# setwd("C:/Users/sony/Desktop/Rmarkdown")
hapdat<- read_xlsx("./happiness.xlsx")
hapdat
```

## Selection Of variables

\normalsize

```{r echo = FALSE, warning=FALSE,message=FALSE}
colnames(hapdat)
ColumnSelected = c(1:3,7:12) 
Happy.df = hapdat[,ColumnSelected]

```

## Summary

\tiny

```{r echo = TRUE, warning=FALSE,message=FALSE}

summary(Happy.df)
DV = Happy.df[,3]
IV = Happy.df[,4:9]

```

## Histogram

```{r echo = FALSE, warning=FALSE,message=FALSE, fig.cap= "Histogram that displays the Social support all regions"}
par(mfrow=c(1,2))
hist(Happy.df$`Social support`)

```

## Plot

```{r echo = FALSE, warning=FALSE,message=FALSE}
fit <- princomp(IV, cor=TRUE)
plot(fit,type="lines") 
fit$scores 

autoplot(fit)

```

```{r echo = FALSE, warning=FALSE,message=FALSE}

Score <- factanal(IV, 3, rotation="varimax")
print(Score, digits=2, cutoff=.3, sort=TRUE)

```

## PLOT 1

```{r  echo = FALSE, warning=FALSE,message=FALSE}

ggpairs(Happy.df[,2:9], mapping = ggplot2::aes(colour=Happy.df$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))

```

## A vector countaining  3 regions & Filter observations only for regions selected

```{r echo = FALSE, warning=FALSE,message=FALSE, fig.align = "center"}
RegionSelected = c("East Asia","Middle East and North Africa","Sub-Saharan Africa")
ImpoReg <- Happy.df %>% filter(`Regional indicator` %in% RegionSelected)
ggpairs(ImpoReg[,2:9], mapping = ggplot2::aes(colour=ImpoReg$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))

ColumnSelected = c("Regional indicator", "Ladder score", "Generosity")
ImpoReg <- ImpoReg %>% select(all_of(ColumnSelected))

summary(ImpoReg)

```

## A vector countaining  1 region

```{r echo = FALSE, warning=FALSE,message=FALSE}
Region = c("Middle East and North Africa")
MENA <- Happy.df %>% filter(`Regional indicator` %in% Region)
ggpairs(MENA[,2:9], mapping = ggplot2::aes(colour=MENA$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))
```

##Happiest & Saddest region 2021 


```{r r echo = FALSE, warning=FALSE,message=FALSE, fig.align = "center"}
Happy.df%>%
  ggplot(aes(Happy.df$`Ladder score`,reorder(Happy.df$`Regional indicator`,Happy.df$`Ladder score`),fill= Happy.df$`Ladder score`))+
  geom_boxplot()+theme_classic()+ theme(legend.position = "none",axis.title.x = element_blank(),axis.title.y = element_blank())+
  scale_fill_brewer(palette = "Set3")+ggtitle(" Happiness_Score_by_Regions ")

```

#life expectancy by region

```{r echo = FALSE, warning=FALSE,message=FALSE, fig.align = "center"}
#life expectancy by region
happy_21%>%
  ggplot(aes(happy_21$`Healthy life expectancy`,reorder(happy_21$`Regional indicator`,happy_21$`Healthy life expectancy`),fill=happy_21$`Regional indicator`))+
  geom_boxplot()+ theme_classic()+ theme(legend.position = "none",axis.title.x = element_blank(),axis.title.y = element_blank())+scale_fill_brewer(palette = "Set3")+ggtitle("Life Expentancy by Regions")

```
