---
title: "World Happiness Report 2021"
author: "Lamiae Harara"
course: "Marketing Practicum"
output:
  beamer_presentation: 
    toc: yes
    theme: AnnArbor
    colortheme: whale
    fonttheme: professionalfonts
    fig_width: 4
    fig_height: 3.5
    fig_caption: yes
    highlight: kate
  ioslides_presentation: default
  slidy_presentation: default
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Table Of Content

* Introduction
* Dataset Description
* 



### Introduction

 \script
 
The World Happiness Report is a landmark survey of the state of global happiness .
The report continues to gain global recognition as governments, organizations and civil society increasingly use happiness indicators to inform their policy-making decisions. Leading experts across fields – economics, psychology, survey analysis, national statistics, health, public policy and more – describe how measurements of well-being can be used effectively to assess the progress of nations. The reports review the state of happiness in the world today and show how the new science of happiness explains personal and national variations in happiness.  
 
 \script

 
### Dataset Description

The happiness scores and rankings use data from the Gallup World Poll . The columns following the happiness score estimate the extent to which each of six factors 
* Economic production
* Social support
* Life expectancy
* Freedom
* Absence of corruption
* Generosity 


## Dataset


```{r echo = FALSE, warning=FALSE,message=FALSE}
library(tidyverse)
library(readxl)
setwd("C:/Users/sony/Desktop/Rmarkdown")
hapdat<- read_xlsx("happiness.xlsx")
hapdat

```

\newpage

## Summary
```{r echo = TRUE, warning=FALSE,message=FALSE}

summary(hapdat)

```

### Selection Of variables
```{r echo = FALSE, warning=FALSE,message=FALSE}
library(tinytex)
library(readr)
colnames(hapdat)
ColumnSelected = c(1:3,7:12) 
Happy.df = hapdat[,ColumnSelected]

```


### Dependent Vs Independent Variables
```{r echo = FALSE, warning=FALSE,message=FALSE}
DV = Happy.df[,3]
IV = Happy.df[,4:9]

```

### PLOT 1


```{r  echo = TRUE, warning=FALSE,message=FALSE}
library(GGally)
library(ggplot2)
ggpairs(Happy.df[,2:9], mapping = ggplot2::aes(colour=Happy.df$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))

```


## Plot2

```{r echo = TRUE, warning=FALSE,message=FALSE}
par(mfrow=c(1,2))
hist(Happy.df$`Social support`)

```

## Plot

```{r echo = TRUE, warning=FALSE,message=FALSE}
fit <- princomp(IV, cor=TRUE)
summary(fit)
loadings(fit) 
plot(fit,type="lines") 
fit$scores 
library(ggfortify)
autoplot(fit)

```


### Plot4

```{r echo = TRUE, warning=FALSE,message=FALSE}
Score <- fit$scores[,1:2]
plot(Score ,type="n") 
text(Score ,labels=names(IV),cex=.7) 

```


### Plot5

```{r echo = TRUE, warning=FALSE,message=FALSE}
library(psych)
Score <- factanal(IV, 3, rotation="varimax")
print(Score, digits=2, cutoff=.3, sort=TRUE)

```

### A vector countaining  3 regions

```{r echo = TRUE, warning=FALSE,message=FALSE}
RegionSelected = c("East Asia","Middle East and North Africa","Sub-Saharan Africa")
ImpoReg <- Happy.df %>% filter(`Regional indicator` %in% RegionSelected)
ggpairs(ImpoReg[,2:9], mapping = ggplot2::aes(colour=ImpoReg$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))
```

### A vector countaining  1 region

```{r echo = TRUE, warning=FALSE,message=FALSE}
Region = c("Middle East and North Africa")
MENA <- Happy.df %>% filter(`Regional indicator` %in% Region)
ggpairs(MENA[,2:9], mapping = ggplot2::aes(colour=MENA$`Regional indicator`), 
        lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))
```